Material Methods

### 2019-09-26 doc/MatMeth_home.Rmd
renamed file for merge conflict

Measures of meiotic chromosomes generated by using ImageJ/Fiji (v1.52) [@fiji].

@@

Statistical analysis was performed in R (v3.5.2)[@Rstudio].

The distributions of CO counts per cell was assessed for normailty (supplemental figure). Mouse mean MLH1 count was used to get around the bad discreet nature of count data. (normality was confirmed with X distribution, supplemental figure).

We choose to use a **mixed model framework** to interpert the patterns of variation. For interperting patterns of mean MLH1 count within and between house mouse subspecies.

1. write equation

$X \sim mouse average MLH1 ~ sex * subspecies + random(strain) + \xi $

In this model
mixed model, observations of mouse means of mlh1, all data with both male and female observations

The main effects and the interaction of subspecies and sex were coded as fixed.

Subspecies, sex and subsp*sex are fixed effects

Strain was coded as a random effect, since in this experimental design we consider it as a sample of natural genetic variation for each subspecies. We also included a term to allow for strains to have a specific sex effect.

This model allows us to estimate and test the fixed effects (sex and subsp), and variation in mean MLH1 counts due to strain effect.

We use the subspecies term as a way to quantify between group variation (or divergence) and the random strain effect to quantify within group variation (or polymorphism). (in a sex specific manner)

@@

I may have to do more research/reading on testing the random effects.
-specific statistical tests; (means, non-parametric kurts wallis t-test?) (correlation coefficient (function))
linear models lm() from X package.
-specific R packages
-non-parametric  (tests and measures for dealing with count data)
-hypothesis tested (size, DSB number)

Comparison/analysis of variation in MLH1 counts within and between groups was done within a general linear/ mix model frame work, using X package (cite).
With X formula Co count ~ blah + blah, with random strain specific sex effect.

(we used this frame work as proxy for 'polymorphism' and 'divergence' in MLH1 counts across house mouse and closely related species.)

>>>>

Hand measures data set generated by using ImageJ/Fiji (v1.52) [@fiji].

@@

0. discribe basic assesment and comparison of MLH1 means (and how it is proxy for genome wide recombination rates)
- assessment and treatment of data quality control ect (correlation measured X)

The distributions of CO counts per cell was assessed for normailty (supplemental figure). Mouse mean MLH1 count was used to get around the bad discreet nature of count data. (normality was confirmed with X distribution, supplemental figure). <re-write this dumb paragraph>

Statistical analysis was performed in R (v3.5.2)[@Rstudio]. mixed models use lmer4 package (cite)

1. framework for analyzing the MLH1 evolutionary patterns across mus species complex. (what is the main question we were tackling when designing this framework?)

2. write equation, discribe terms (proxies for within and between polymorphsm)
logic / choices for fixed and random effects

3. what are the 2 general / basic questions this framework can be applied to.

$X \sim mouse average MLH1 ~ sex + subspecies + random(strain) + \xi $
< can't get the equation in the right format. I think this breaks the pdf kniting.>

4. how can DMC1 measures be added to the mixed model

5. discriptions of mlh1 outside of framework (missing female data)

mixed model, observations of mouse means of mlh1, all data with both male and female observations

subspecies, sex and subsp*sex are fixed effects
strain as random effect (sample of a genetic background from subspecies)
with domesticus male set as the default

strain and sex interaction effect was included to ask / test if the effect of sex varies by strain(genetic background)

this model allows us to estimate and test the fixed effects (sex and subsp)

the random effect of strain in this model can be interpreted as the average standard deviation due to the random strain effect
and sex  strain,

@@

I may have to do more research/reading on testing the random effects.

-specific statistical tests; (means, non-parametric kurts wallis t-test?) (correlation coefficient (function))
linear models lm() from X package.

Comparison/analysis of variation in MLH1 counts within and between groups was done within a general linear/ mix model frame work, using X package (cite).
(we used this frame work as proxy for 'polymorphism' and 'divergence' in MLH1 counts across house mouse and closely related species.)
